Through the eyes of the teacher

### 2021-03-17 paper_1/paper_1_supplement_et_aoi.Rmd
update plots GRI

# if a package is not installed on the current machine, it will install it
if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
if (!require(papaja)) install.packages('papaja'); library(papaja)
if (!require(psych)) install.packages('psych'); library(psych) # stats
if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index

@@

### Questionnaire data

After each mini-lesson, the students answered items on the teaching quality using a validated questionnaire [@helmke2014unterrichtsdiagnostik] and scales on the teacher's presence behavior (students n = 24). In addition, the teacher was asked to give a self-assessment on his/her classroom management by completing the questionnaire after each mini-lesson (teachers n = 8).

### Behavioral data

The speech, sounds and voices were recorded with an audio recorder installed in the middle of the Lab. Movements, facial expressions and gestures of the subjects were recorded by four cameras from different angles. One camera was installed to film the class from the side. Two more cameras were installed on the blackboard and at the end of the Lab to film the teacher and class from the front and back. Furthermore, the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.

@@

### Questionnaire Data

The evaluation after each mini-lesson was conducted using paper questionnaires. Time needed to complete the questionnaire was about 5 minutes. 
The scales on the quality of teaching are a validated questionnaire [@helmke2014unterrichtsdiagnostik]. Whereas the scales on the teacher's presence behavior were derived from the research literature [@brophy1986classroom; @kiel2013trainingsbuch; @kounin2006techniken; @marzano2007art; @nolting2012storungen] and were used in the pilot for the first time. The questionnaire is 4-point Likert scale (1 = Strongly Disagree; 2 = Disagree; 3 = Agree; 4 = Strongly Agree). Data was obtained from N = 32 subjects (students n = 24, teachers n = 8).

The following scales were assessed:

(1) Classroom management
(2) Positive climate and motivation
(3) Clarity and structuredness
(4) Activation and support
(5) Presence: posture/gaze
(6) Presence: voice
(7) Presence: verbal and non-verbal intervention
(8) Natural behaviour

Table \@ref(tab:table-all-scales-self-assessment) provides an overview over the mean, the standard deviation, the range, Cronbach's Alpha and the Skewness & Kurtosis of all scales for the teachers' self-assessment.

```{r table-all-scales-self-assessment, echo=FALSE, message=FALSE, warning=FALSE}

# prepare data (selected from questionnaire data) - only equal items and without observer
quest.raw.data<-read.table("./data/short_questionnaire_data_150221.txt", dec=",", sep="\t", header=T)

# knock out NAs and duration of speaking time
quest.raw.data <- quest.raw.data  %>% filter(
  personID != "NA",
  itemID != "8",
  perspective == "self-assessment")

# value sometimes contained text before filtering, we have to convert the numbers to numeric
quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(value))

##############################################

# calculate Cronbach's Alpha for each scale
# activation & support
self.as.wide <- quest.raw.data %>%
                          filter (scale == "Activation and support") %>%  
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)
self.alpha.as <- alpha(self.as.wide[,-1])

#clarity & structuredness
self.cs.wide <- quest.raw.data %>%
                          filter (scale == "Clarity and structuredness") %>%  
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

self.alpha.cs <- alpha(self.cs.wide[,-1])

#classroom management
self.cm.wide <- quest.raw.data %>%
                          filter (scale == "Classroom management") %>%  
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

self.alpha.cm <- alpha(self.cm.wide[,-1])

#natural behaviour
self.nb.wide <- quest.raw.data %>%
                          filter (scale == "Natural behaviour") %>%  
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

self.alpha.nb <- alpha(self.nb.wide[,-1])

#positive climate and motivation
self.pcm.wide <- quest.raw.data %>%
                          filter (scale == "Positive climate and motivation") %>%  
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

self.alpha.pcm <- alpha(self.pcm.wide[,-1])

#presence: posture & gaze
self.ppg.wide <- quest.raw.data %>%
                          filter (scale == "Presence: posture/gaze") %>%  
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

self.alpha.ppg <- alpha(self.ppg.wide[,-1])

#presence: voice
self.pv.wide <- quest.raw.data %>%
                          filter (scale == "Presence: voice") %>%  
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

self.alpha.pv <- alpha(self.pv.wide[,-1])

#presence: verbal/non-verbal intervention
self.pvni.wide <- quest.raw.data %>%
                          filter (scale == "Presence: verbal and non-verbal intervention") %>%  
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

self.alpha.pvni <- alpha(self.pvni.wide[,-1])

#Presence without subscales
self.p.wide <- quest.raw.data %>%
                          filter(str_detect(scale,
                                        paste(c(
                                        "Presence: voice", 
                                        "Presence: verbal and non-verbal intervention", 
                                        "Presence: posture/gaze"),
                                         collapse = '|'))) %>% 
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

self.alpha.p <- alpha(self.p.wide[,-1])

##############################################

# # item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
# 
# # activation & support
# tab_itemscale(self.as.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # classroom management
# tab_itemscale(self.cm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # clarity & structuredness
# tab_itemscale(self.cs.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # natural behaviour
# tab_itemscale(self.nb.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # postive clima and motivation
# tab_itemscale(self.pcm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # presence without subscales
# tab_itemscale(self.p.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # presence: posture & gaze
# tab_itemscale(self.ppg.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# # presence: voice
# tab_itemscale(self.pv.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# # presence: verbal/non-verbal intervention
# tab_itemscale(self.pvni.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)

##############################################

# add alphas to excel table 
# read in new data 
quest.raw.data.alpha <- read.table("./data/short_questionnaire_data_260221_alpha.txt", dec=",", sep="\t", header=T)

# value sometimes contained text before filtering, we have to convert the numbers to numeric
quest.raw.data.alpha <- quest.raw.data.alpha %>%  mutate(alpha = as.numeric(alpha))

##############################################

# #####correlation between all presences' items
# SELF-ASSESSMENT
# install.packages("Hmisc")
# library("Hmisc")

# function cr() to format the correlation matrix
res1.self<-cor(self.p.wide[,-1])

# Visualization correlation matrix
# Use corrplot() function: Draw a correlogram

# # install.packages("corrplot")
# library("corrplot")
# 
# # Insignificant correlation are crossed
# corrplot(res1.self$r, type="upper", order="hclust",
#          p.mat = res1.self$P, sig.level = 0.01, insig = "blank")
# # Insignificant correlations are leaved blank
# corrplot(res1.self$r, type="upper", order="hclust",
#          p.mat = res1.self$P, sig.level = 0.01, insig = "blank")

###############################################

# create a basic table (tibble) using tidyverse functions for teachers' self assessment 
# Change Number of Digits in Global R Options to reduce the number of digits after the decimal point to two
options(digits = 2)

teacher.scale.quest.table <- quest.raw.data.alpha %>% # select data
  filter(perspective == "self-assessment")%>%
  group_by(scale) %>%
  summarise("N items" = n_distinct(shortID),
            "M" = round(mean(value), 2),
            "SD" = round(sd(value), 2),
            "Min" = min(value),
            "Max" = max(value),
            "Skewness" = skewness(value),
            "Kurtosis" = kurtosis(value),
            "Cronbach's α" = mean(alpha))

# format and insert table in manuscript
apa_table(
  teacher.scale.quest.table,
  caption = "Scale analysis for teachers' self-assessment",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
)

Table \@ref(tab:table-all-scales-students) provides an overview over the mean, the standard deviation, the range, Cronbach's Alpha and the Skewness & Kurtosis of all scales for the students' perception of the teacher's behaviour in class.

```{r table-all-scales-students, echo=FALSE, message=FALSE, warning=FALSE}

# prepare data (selected from questionnaire data) - only equal items and without observer
quest.raw.data<-read.table("./data/short_questionnaire_data_150221.txt", dec=",", sep="\t", header=T)

# knock out NAs and duration of speaking time
quest.raw.data <- quest.raw.data  %>% filter(
  personID != "NA",
  itemID != "8",
  perspective == "student")
view(quest.raw.data)

# value sometimes contained text before filtering, we have to convert the numbers to numeric
quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(value))

###############################################

# calculate Cronbach's Alpha for each scale of students' peception

# activation & support
stud.as.wide <- quest.raw.data %>%
                          filter (scale == "Activation and support") %>%  
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)
stud.alpha.as <- alpha(stud.as.wide[,-1])

#clarity & structuredness
stud.cs.wide <- quest.raw.data %>%
                          filter (scale == "Clarity and structuredness") %>%  
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

stud.alpha.cs <- alpha(stud.cs.wide[,-1])

#classroom management
stud.cm.wide <- quest.raw.data %>%
                          filter (scale == "Classroom management") %>%  
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

stud.alpha.cm <- alpha(stud.cm.wide[,-1])

#natural behaviour
stud.nb.wide <- quest.raw.data %>%
                          filter (scale == "Natural behaviour") %>%  
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

stud.alpha.nb <- alpha(stud.nb.wide[,-1])

#positive climate and motivation
stud.pcm.wide <- quest.raw.data %>%
                          filter (scale == "Positive climate and motivation") %>%  
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

stud.alpha.pcm <- alpha(stud.pcm.wide[,-1])

#presence: posture & gaze
stud.ppg.wide <- quest.raw.data %>%
                          filter (scale == "Presence: posture/gaze") %>%  
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

stud.alpha.ppg <- alpha(stud.ppg.wide[,-1])

#presence: verbal and non-verbal intervention
stud.pvni.wide <- quest.raw.data %>%
                          filter (scale == "Presence: verbal and non-verbal intervention") %>%  
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

stud.alpha.pvni <- alpha(stud.pvni.wide[,-1])

#presence: voice
stud.pv.wide <- quest.raw.data %>%
                          filter (scale == "Presence: voice") %>%  
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

stud.alpha.pv <- alpha(stud.pv.wide[,-1])

#Presence without subscales
stud.p.wide <- quest.raw.data %>%
                          filter(str_detect(scale,
                                        paste(c(
                                        "Presence: voice", 
                                        "Presence: verbal and non-verbal intervention", 
                                        "Presence: posture/gaze"),
                                         collapse = '|'))) %>% 
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

stud.alpha.p <- alpha(stud.p.wide[,-1])

# ###############################################

# # item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
# 
# # activation & support
# tab_itemscale(stud.as.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # classroom management
# tab_itemscale(stud.cm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # clarity & structuredness
# tab_itemscale(stud.cs.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # natural behaviour
# tab_itemscale(stud.nb.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # positive clima and motivation
# tab_itemscale(stud.pcm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # presence without subscales
# tab_itemscale(stud.p.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # presence: posture & gaze
# tab_itemscale(stud.ppg.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# # presence: voice
# tab_itemscale(stud.pv.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# # presence: verbal/non-verbal intervention
# tab_itemscale(stud.pvni.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)

##############################################
# #####correlation between all presences' items
# SELF-ASSESSMENT
# install.packages("Hmisc")
library("Hmisc")

# # function to format the correlation matrix
# flattenCorrMatrix <- function(cormat, pmat) {
#   ut <- upper.tri(cormat)
#   data.frame(
#     row = rownames(cormat)[row(cormat)[ut]],
#     column = rownames(cormat)[col(cormat)[ut]],
#     cor  =(cormat)[ut],
#     p = pmat[ut]
#     )
# }
# 
# res1.stud<-cor(stud.p.wide[,-1])

# res1.stud<-rcorr(as.matrix(stud.p.wide[,-1]))
# 
# flattenCorrMatrix(res1.stud$r, res1.stud$P)
# 
# res2.stud<-flattenCorrMatrix(res1.stud$r, res1.stud$P)

# Visualization correlation matrix
# Use corrplot() function: Draw a correlogram

# install.packages("corrplot")
library("corrplot")

# # Insignificant correlation are crossed
# corrplot(res1.stud$r, type="upper", order="hclust",
#          p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
# # Insignificant correlations are leaved blank
# corrplot(res1.stud$r, type="upper", order="hclust",
#          p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")

##############################################

# add alphas to excel table 
# read in new data 
quest.raw.data.alpha <- read.table("./data/short_questionnaire_data_260221_alpha.txt", dec=",", sep="\t", header=T)

# value sometimes contained text before filtering, we have to convert the numbers to numeric
quest.raw.data.alpha <- quest.raw.data.alpha %>%  mutate(alpha = as.numeric(alpha))

##############################################

# create a basic table (tibble) using tidyverse functions for teacher self assessment 
student.scale.quest.table <- quest.raw.data.alpha %>% # select data
  filter(perspective == "student")%>%
  group_by(scale) %>%
  summarise("N items" = n_distinct(shortID),
            "M" = round(mean(value), 2),
            "SD" = round(sd(value), 2),
            "Min" = min(value),
            "Max" = max(value),
            "Skewness" = skewness(value),
            "Kurtosis" = kurtosis(value),
            "Cronbach's α" = mean(alpha))

# format and insert table in manuscript
apa_table(
  student.scale.quest.table,
  caption = "Scale analysis for students' perspective",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
)

\newpage
The individual items of a scale are further represented in graphs.

(1) Classroom management
```{r Line Plots Classroom Management, echo=FALSE, fig.height=6, fig.width=6, message=FALSE, warning=FALSE, fig.cap="Items for Classroom Management"}

### classroom management

# filter by parameter variable, i.e. create a subset for classroom management without perspective "observer"
cm.data <- quest.raw.data %>% filter(scale == "Classroom management")

view(cm.data)

# value sometimes contained text before filtering, we have to convert the numbers to numeric
cm.data <- cm.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# to create error bars, we need to summarize the data in a separate data frame
cm.plot.sd <- cm.data %>%
  group_by(group, item.wordings, .drop=TRUE) %>%
  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# long plot
cm.plot<-ggplot(data = cm.plot.sd,
                  aes(x = item.wordings, y = mean,
                      group = perspective, colour = perspective)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  facet_grid(~perspective)+
  labs(data = cm.data, y = "value", x = NULL,
       title="Classroom management" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 6))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
cm.plot

```
\newpage
(2) Positive climate and motivation
```{r Positive climate and motivation line plots,  fig.width=6, fig.height = 7, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Positive climate and motivation"}

### Positive climate and motivation

# filter by parameter variable, i.e. create a subset for Positive climate and motivation
pcm.data <- quest.raw.data %>% filter(scale == "Positive climate and motivation")

# value sometimes contained text before filtering, we have to convert the numbers to numeric
pcm.data <- pcm.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# to create error bars, we need to summarize the data in a separate data frame
pcm.plot.sd <- pcm.data %>%
  group_by(group, item.wordings, .drop=TRUE) %>%
  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# long plot
pcm.plot<-ggplot(data = pcm.plot.sd,
                  aes(x = item.wordings, y = mean,
                      group = group, colour = group)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  facet_grid(~perspective)+
  labs(data = pcm.data, y = "value", x = NULL,
       title="Positive climate and motivation" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 5))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
pcm.plot

```
\newpage
(3) Clarity and structuredness
```{r Clarity and structuredness line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Clarity and structuredness"}

### Clarity and structuredness

# filter by parameter variable, i.e. create a subset for Clarity and structuredness
cs.data <- quest.raw.data %>% filter(scale == "Clarity and structuredness")

# value sometimes contained text before filtering, we have to convert the numbers to numeric
cs.data <- cs.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# to create error bars, we need to summarize the data in a separate data frame
cs.plot.sd <- cs.data %>%
  group_by(group, item.wordings, .drop=TRUE) %>%
  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# long plot
cs.plot<-ggplot(data = cs.plot.sd,
                  aes(x = item.wordings, y = mean,
                      group = group, colour = group)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  facet_grid(~perspective)+
  labs(data = cs.data, y = "value", x = NULL,
       title="Clarity and structuredness" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 6))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
cs.plot

```
\newpage
(4) Activation and support
```{r Activation and support line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Activation and support"}

### Activation and support

# filter by parameter variable, i.e. create a subset for Activation and support
as.data <- quest.raw.data %>% filter(scale == "Activation and support")

# value sometimes contained text before filtering, we have to convert the numbers to numeric
as.data <- as.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# to create error bars, we need to summarize the data in a separate data frame
as.plot.sd <- as.data %>%
  group_by(group, item.wordings, .drop=TRUE) %>%
  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# long plot
as.plot<-ggplot(data = as.plot.sd,
                  aes(x = item.wordings, y = mean,
                      group = group, colour = group)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  facet_grid(~perspective)+
  labs(data = as.data, y = "value", x = NULL,
       title="Activation and support" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 6))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
as.plot

```
\newpage

(ref:presenceposturegaze-caption) (5) Presence: posture/gaze

```{r presenceposturegaze, fig.cap = "(ref:presenceposturegaze-caption)", fig.align = "center", echo = FALSE}

knitr::include_graphics("./pictures/presenceposturegaze.png", dpi = 108)

# ```{r Presence: posture/gaze line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}

# ### Presence: posture/gaze 
# 
# # filter by parameter variable, i.e. create a subset for Presence: posture/gaze
# ppg.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")
# 
# # value sometimes contained text before filtering, we have to convert the numbers to numeric
# ppg.data <- ppg.data %>%  mutate(value = as.numeric(as.character(factor(value))))
# 
# # to create error bars, we need to summarize the data in a separate data frame
# ppg.plot.sd <- ppg.data %>%
#   group_by(group, item.wordings, .drop=TRUE) %>%
#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
# 
# # long plot
# ppg.plot<-ggplot(data = ppg.plot.sd,
#                   aes(x = item.wordings, y = mean,
#                       group = group, colour = group)) +
#   geom_line()+
#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
#   theme_light() +
#   ylim(1,4)+
#   facet_grid(~perspective)+
#   labs(data = ppg.data, y = "value", x = NULL,
#        title="Presence: posture/gaze" ,
#        subtitle=NULL)+
#   theme(legend.position="bottom",
#         panel.spacing.x = ,
#         plot.title = element_text(hjust = 0.5),
#         axis.text.y = element_text(size = 6))+
#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
#   coord_flip()
# ppg.plot

(ref:presencevoice-caption) (6) Presence: voice

```{r presencevoice, fig.cap = "(ref:presencevoice-caption)", fig.align = "center", echo = FALSE}

knitr::include_graphics("./pictures/presencevoice.png", dpi = 108)

# ```{r Presence: voice line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
# 
# ### Presence: voice 
# # filter by parameter variable, i.e. create a subset for Presence: voice
# pv.data <- quest.raw.data %>% filter(scale == "Presence: voice")
# 
# # value sometimes contained text before filtering, we have to convert the numbers to numeric
# pv.data <- pv.data %>%  mutate(value = as.numeric(as.character(factor(value))))
# 
# # to create error bars, we need to summarize the data in a separate data frame
# pv.plot.sd <- pv.data %>%
#   group_by(group, item.wordings, .drop=TRUE) %>%
#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
# 
# # long plot
# pv.plot<-ggplot(data = pv.plot.sd,
#                   aes(x = item.wordings, y = mean,
#                       group = group, colour = group)) +
#   geom_line()+
#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
#   theme_light() +
#   ylim(1,4)+
#   facet_grid(~perspective)+
#   labs(data = pv.data, y = "value", x = NULL,
#        title="Presence: voice" ,
#        subtitle=NULL)+
#   theme(legend.position="bottom",
#         panel.spacing.x = ,
#         plot.title = element_text(hjust = 0.5),
#         axis.text.y = element_text(size = 6))+
#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
#   coord_flip()
# pv.plot

```
\newpage

(ref:presenceverbalnonverbalintervention-caption) (7) Presence: verbal and non-verbal intervention

```{r presenceverbalnonverbalintervention, fig.cap = "(ref:presenceverbalnonverbalintervention-caption)", fig.align = "center", echo = FALSE}

knitr::include_graphics("./pictures/presenceverbalnonverbalintervention.png", dpi = 108)

# ```{r Presence: verbal and non-verbal intervention line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
# 
# ### Presence: verbal and non-verbal intervention 
# # filter by parameter variable, i.e. create a subset for Presence: verbal and non-verbal intervention
# pvni.data <- quest.raw.data %>% filter(scale == "Presence: verbal and non-verbal intervention")
# 
# # value sometimes contained text before filtering, we have to convert the numbers to numeric
# pvni.data <- pvni.data %>%  mutate(value = as.numeric(as.character(factor(value))))
# 
# # to create error bars, we need to summarize the data in a separate data frame
# pvni.plot.sd <- pvni.data %>%
#   group_by(group, item.wordings, .drop=TRUE) %>%
#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
# 
# # long plot
# pvni.plot<-ggplot(data = pvni.plot.sd,
#                   aes(x = item.wordings, y = mean,
#                       group = group, colour = group)) +
#   geom_line()+
#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
#   theme_light() +
#   ylim(1,4)+
#   facet_grid(~perspective)+
#   labs(data = pvni.data, y = "value", x = NULL,
#        title="Presence: verbal and non-verbal intervention" ,
#        subtitle=NULL)+
#   theme(legend.position="bottom",
#         panel.spacing.x = ,
#         plot.title = element_text(hjust = 0.5),
#         axis.text.y = element_text(size = 6))+
#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
#   coord_flip()
# pvni.plot

```
\newpage
(8) Natural behaviour
```{r Natural behaviour line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Natural Behaviour"}

### Natural behaviour 
# filter by parameter variable, i.e. create a subset for Natural behaviour
nb.data <- quest.raw.data %>% filter(scale == "Natural behaviour")

# value sometimes contained text before filtering, we have to convert the numbers to numeric
nb.data <- nb.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# to create error bars, we need to summarize the data in a separate data frame
nb.plot.sd <- nb.data %>%
  group_by(group, item.wordings, .drop=TRUE) %>%
  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# long plot
nb.plot<-ggplot(data = nb.plot.sd,
                  aes(x = item.wordings, y = mean,
                      group = group, colour = group)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  facet_grid(~perspective)+
  labs(data = nb.data, y = "value", x = NULL,
       title="Natural behaviour" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 6))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
nb.plot

```
\newpage
In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.

```{r boxplot scales, fig.width=6, fig.height = 8, echo = FALSE, fig.cap = "Boxplots and individual data for experts and novices"}

quest.plot <- quest.raw.data %>%
  ggplot(aes(x=scale, y=value, fill=scale)) +
    geom_boxplot() +
    scale_x_discrete(guide = guide_axis(angle = 70)) +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    theme_light() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    facet_grid(~group)+
    ggtitle("Boxplot with individual points for all scales") +
    xlab("")
quest.plot

### Behavioral Data

The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters [@kuckartz2019analyzing]. The following coding scheme was developed:

- phase - lesson begin, state event: teacher starts the lesson with a noise, talk, taking a position in class
- phase - lesson end,	state event: teacher finishes the lesson with a noise, talk, taking a position in class
- phase - organization/transition points, state event: any situation that does not imply effective learning time (fetching chalk, working        material, organizing desks, opening windows, printing work results etc.)
- phase - single,	state event: any individual student activity on a given task (reading, writing, drawing etc.)
- phase - group, state event: any student activity on a given task together in a group of at least 3 students (reading, writing, drawing etc.)
- phase - class discussion, state event: discussion in class, teacher talks to class/individual/group
- phase - pair: state event: any student activity on a given task together in a team of 2 students (reading, writing, drawing etc.)
- phase - teachers lecture, state event: any teacher's presentation on a certain topic which maybe supported by a PPP, PREZI, notes on board,    OHP etc.
- phase - other, state event: not categorizable
- phase - break, state event: e.g. drinking, relaxation exercises
- phase - external interruption, state event: external interruptions (e.g. fire alarm, technical problems, other teachers coming into the room)

- speaking time - teacher, state event
- speaking time - students, state event

- disruption - chatting with neighbor, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - asking a question, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - yelling, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - looking at phone, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - staring out of window, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - drawing, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - head on table, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - clicking pen, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - drumming hands, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - walking around, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)

First, we coded the speaking time of the teacher and the students to compare all perspectives: coder, observer, students, teacher. The graph below shows the result of the coded speaking duration compared to the estimated speaking duration assessed with the questionnaire.

```{r coded speaking time, echo = FALSE }
### read in data for 01_01_expert_D
speaking.data.01.01 <- read.delim("./data/Aperol_pilot_01_01_expert_D_cam4_AL_MK.txt", dec=",", sep="\t", header=T)

### select relevant columns
speaking.data.01.01 <- speaking.data.01.01  %>% select(
  Dokumentgruppe,
  Dokumentname,
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

### filter only speaking time of teacher and "kodiert von Anna" as row 
speaking.data.01.01 <- speaking.data.01.01 %>% filter (Code == "speaking time\\teacher",
                                           Dokumentgruppe == "kodiert von Anna")
speaking.data.01.01 <- sum(speaking.data.01.01$Abdeckungsgrad..)

>>>>

# if a package is not installed on the current machine, it will install it
if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")
if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
if (!require(papaja)) install.packages("papaja"); library(papaja)
if (!require(psych)) install.packages('psych'); library(psych) # stats
if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index

@@

@@
